### 2015-07-15 src/misc/s7_series_list.tex
Updated Donders series.

	{Utrecht University}{Utrecht}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Impact of nutritional lipids and vascular factors in Alzheimer’s disease.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Waterbath stunning of chickens – Effects of electrical parameters on the electroencephalogram and physical reflexes of broilers.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Cognitive and physiological effects of 3,4-methylenedioxymethamphetamine (MDMA or ’ecstasy’) in combination with alcohol or cannabis in humans.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}
\dientry{28}{Dado – Van Beek, H.E.A.}{2010}
	{The regulation of cerebral perfusion in patients with Alzheimer’s disease.}
	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Memory consolidation: A process of integration – Converging evidence from MEG, fMRI and behavior.}
	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Neural correlates of episodic memory in healthy aging and Alzheimer’s disease.}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}
\dientry{46}{Crajé, C.}{2011}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}
\dientry{51}{Bögels, S.}{2011}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Cerebral reorganization in Parkinson’s disease.}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Development of action perception: Neurocognitive mechanisms underlying children’s processing of others’ actions.}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{‘How one can see what is not there’: Neural mechanisms of grapheme-colour synaesthesia.}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Amyloidogenic proteins in Alzheimer’s disease and Parkinson’s disease: Interaction with chaperones and inflammation.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Measuring the mind’s ear: EEG of music imagery.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

\dientry{72}{Mädebach, A.}{2011}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Utrecht University}{Utrecht}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{}

@@

@@

@@

@@

	{ CSF biomarkers of Alzheimer’s disease: Serial sampling analysis and the study of circadian rhythmicity.}
	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

@@

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}
\dientry{103}{Wingbermühle, E.}{2012}

@@

@@

@@

@@

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

@@

@@

@@

@@

\dientry{115}{Böckler, A.}{2013}
	{Looking at the world together. How others’ attentional relations to jointly attended scenes shape cognitive processing.}

@@

@@

@@

@@

@@

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{}

@@

	{On the conceptual and perceptual processing of own and others’ behavior.}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}

@@

@@

@@

	{University of Twente}{Enschede}{The Netherlands}{}

@@

@@

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}

@@

@@

@@

@@

\dientry{138}{Lüttjohann, A.K.}{2013}

@@

	{Change doesn’t come easy: Dynamics of adaptive behavior in psychopathy.}

@@

@@

@@

@@

@@

@@

@@

@@

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}

@@

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}

@@

@@

@@

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{}
\dientry{171}{Leoné, F.T.M.}{2014}

@@

	{Radboud University Medical Centre}{Nijmegen}{The Netherlands}{}

@@

@@

	{“Inbetween Modalitiers combined EEG – fMR”.}

@@

@@

@@

@@

@@

@@

>>>>

	{Utrecht University}{Utrecht}{the Netherlands}{2066/78656}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/73422}

@@

	{Impact of nutritional lipids and vascular factors in Alzheimer's disease.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/71190}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/65578}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/65547}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/76949}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/77171}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/76950}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/83282}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/77395}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/80506}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/77060}

@@

	{Waterbath stunning of chickens - Effects of electrical parameters on the electroencephalogram and physical reflexes of broilers.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/77181}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/77308}

@@

	{Cognitive and physiological effects of 3,4-methylenedioxymethamphetamine (MDMA or 'ecstasy') in combination with alcohol or cannabis in humans.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/74937}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/76508}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/76507}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/76514}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/76177}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/74943}
\dientry{28}{Dado - Van Beek, H.E.A.}{2010}
	{The regulation of cerebral perfusion in patients with Alzheimer's disease.}
	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/76550}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/83823}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/76518}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/86659}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/87824}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/90514}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/90729}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/77569}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/82609}

@@

	{Memory consolidation: A process of integration - Converging evidence from MEG, fMRI and behavior.}
	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/115475}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/79438}

@@

	{Neural correlates of episodic memory in healthy aging and Alzheimer's disease.}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/82967}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/83223}
\dientry{46}{Craj\'e, C.}{2011}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/83193}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/84479}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/83241}
\dientry{51}{B\"ogels, S.}{2011}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/115507}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/91774}

@@

	{Cerebral reorganization in Parkinson's disease.}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/91455}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/87188}

@@

	{Development of action perception: Neurocognitive mechanisms underlying children's processing of others' actions.}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/90816}

@@

	{'How one can see what is not there': Neural mechanisms of grapheme-colour synaesthesia.}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/90927}

@@

	{Amyloidogenic proteins in Alzheimer's disease and Parkinson's disease: Interaction with chaperones and inflammation.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/90826}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/91217}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/97180}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/91291}

@@

	{Measuring the mind's ear: EEG of music imagery.}
	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/90929}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/91338}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/91248}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/90931}

@@

\dientry{72}{M\"adebach, A.}{2011}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/91242}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/91312}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/97730}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/91340}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/91390}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/92727}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/91441}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/102727}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/93538}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/93525}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/102871}

@@

	{Utrecht University}{Utrecht}{the Netherlands}{1874/234838}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/93575}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/93547}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/108820}

@@

	{Radboud University Nijmegen}{Nijmegen}{the Netherlands}{2066/93600}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/98578}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/102847}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/102755}

@@

	{ CSF biomarkers of Alzheimer's disease: Serial sampling analysis and the study of circadian rhythmicity.}
	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/110459}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/107952}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/100885}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/110168}
\dientry{103}{Wingberm\"uhle, E.}{2012}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/101058}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/99162}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/101056}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/106937}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/109595}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/105807}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/100904}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/105839}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/102405}

@@

\dientry{115}{B\"ckler, A.}{2013}
	{Looking at the world together. How others' attentional relations to jointly attended scenes shape cognitive processing.}
	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/116565}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/107679}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/116538}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/116598}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/118661}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/121283}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{the Netherlands}{2066/115717}

@@

	{On the conceptual and perceptual processing of own and others' behavior.}
	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/116593}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/113037}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/115716}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/121139}

@@

	{University of Twente}{Enschede}{The Netherlands}{2066/124111}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/112928}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/112927}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/113033}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/120020}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/116595}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/125605}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/112935}
\dientry{138}{L\"uttjohann, A.K.}{2013}

@@

	{Change doesn't come easy: Dynamics of adaptive behavior in psychopathy.}
	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/115727}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/120593}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/119670}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/124136}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/126370}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/127799}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/129404}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/129470}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/126371}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/125600}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/127383}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/127514}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/127114}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/127776}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/127118}

@@

	{Radboud University Nijmegen}{Nijmegen}{The Netherlands}{2066/135138}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/128280}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/127366}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/130300}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/130290}

@@

	{Radboud University Nijmegen Medical Centre}{Nijmegen}{The Netherlands}{2066/132065}
\dientry{171}{Leon\'e, F.T.M.}{2014}

@@

	{Radboud University Medical Centre}{Nijmegen}{The Netherlands}{2066/132628}

@@

	{Radboud University}{Nijmegen}{The Netherlands}{2066/139139}

@@

	{'Inbetween Modalitiers combined EEG - fMRI'.}

@@

	{Radboud university medical center}{Nijmegen}{The Netherlands}{2066/135625}

@@

	{Radboud university medical center}{Nijmegen}{The Netherlands}{2066/140091}

@@

	{Radboud University}{Nijmegen}{The Netherlands}{2066/138588}

@@

	{Radboud university medical center}{Nijmegen}{The Netherlands}{2066/141370}

@@

	{Radboud university medical center}{Nijmegen}{The Netherlands}{2066/141389}

@@

	{Radboud University}{Nijmegen}{The Netherlands}{2066/141050}
